### 2021-07-15 doc/thesis/chapters/implementation.tex
new block diagram - vhdl testbench architecture

Fig.\ref{fig:bd_vhdl_implemented_tb_architecture} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual interfaces, as described in \ref{sub:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

\includepicture [1.0] [0]  {Block diagram of the implemented testbench architecture.} {bd_vhdl_implemented_tb_architecture} {img/draw.io/bd_vhdl_implemented_tb_architecture}

>>>>

Fig.\ref{fig:bd_testbench_architecture_vhdl} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual interfaces, as described in \ref{sub:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

\includepicture [1.0] [0]  {Block diagram of the implemented testbench architecture.} {bd_testbench_architecture_vhdl} {img/draw.io/bd_testbench_architecture_vhdl}
